Tor's Usability for Censorship Circumvention

### 2016-04-05 pets2017-paper/pets2017-paper.tex
mark undone red
Add labels to figures.
Include time_to_success_ecdf figure.

%skip talking about the process of redesigning the interface. It isn't that interesting.

@@

The design is a conservative design which accounts for at-risk users, backward compatibility, and maintainability.

@@

\begin{figure}
\centering
\includegraphics{time_to_success}
\caption{
Time to first success, by censorship environment and interface.
The dots show the raw completion times;
while the boxplots show the medians and interquartile ranges.
The ``DNF'' figures at the right
show the number of participants who did not finish
in the time alloted.
}
\end{figure}

\begin{figure}
\centering
\includegraphics{time_to_success_clamped}
\caption{
Time to first success, by censorship environment and interface.
Here, non-finishing participants are assigned a time of 40 minutes.
}
\end{figure}

>>>>

%skip talking about the process of redesigning the interface. It isn't that interesting. 
{\color {red}

@@

The design is a conservative design which accounts for at-risk users, backward compatibility, and maintainability. 
}

@@

\begin{figure}
\centering
\includegraphics{time_to_success}
\caption{
Time to first success, by censorship environment and interface.
The dots show the raw completion times;
while the boxplots show the medians and interquartile ranges.
The ``DNF'' figures at the right
show the number of participants who did not finish
in the time alloted.
}
\label{fig:time_to_success}
\end{figure}

\begin{figure}
\centering
\includegraphics{time_to_success_clamped}
\caption{
Time to first success, by censorship environment and interface.
Here, non-finishing participants are assigned a time of 40 minutes.
}
\label{fig:time_to_success_clamped}
\end{figure}

\begin{figure}
\centering
\includegraphics{time_to_success_ecdf}
% From info.R:
% success rate of E1-NEW after 1m30.0s: 100.0%
% success rate of E1-OLD after 1m30.0s:  57.9%
% success rate of E2-NEW after 10m00.0s:  78.9%
% success rate of E2-OLD after 10m00.0s:  68.4%
% success rate of E3-NEW after 10m00.0s:  25.0%
% success rate of E3-OLD after 10m00.0s:  20.0%
% success rate of E2-NEW after 20m00.0s:  89.5%
% success rate of E2-OLD after 20m00.0s:  78.9%
% success rate of E3-NEW after 20m00.0s:  45.0%
% success rate of E3-OLD after 20m00.0s:  25.0%
\caption{
Cumulative success rates over time.
We stopped participants after 40 minutes;
this graph shows what the success rate would have been
at different cutoff times.
For example, every E1-NEW participant finished within 90 seconds,
but only 58\% of E1-OLD had finished by that time.
After 10 minutes, 79\% of E2-NEW and 68\% of E2-OLD had finished.
After 20 minutes, 45\% of E3-NEW and only 25\% of E3-OLD had finished.
}
\label{fig:time_to_success_ecdf}
\end{figure}
